Migration of Gas Giant Planets in Gravitationally Unstable Disks

### 2011-06-07 Text/migration_apjlsubmission.tex
Final submitted version of the migration letter.
	modified:   Text/Figures/amt.eps
	new file:   Text/Figures/amt_bw.eps
	modified:   Text/Figures/planeta.eps
	deleted:    Text/Figures/planeta.pdf
	new file:   Text/Figures/planeta_bw.eps
	modified:   Text/Figures/planete.eps
	deleted:    Text/Figures/planete.pdf
	new file:   Text/Figures/planete_bw.eps
	modified:   Text/general.bib
	modified:   Text/migration.tex
	copied:     Text/migration.tex -> Text/migration_apjlsubmission.tex

git-svn-id: http://jaga.astro.indiana.edu/paperrepo/ApJL/Migration2010@86 3b7f7548-5c66-0410-83ab-3997167635fc

\bibliographystyle{apj}
\bibliography{general}

@@

%***DICK: Scott, remember that figures need some improvements.

\begin{figure}[t]
\center
\includegraphics[width=11cm]{Figures/amt.eps}
\caption{(Color figure available in the online version) Global amplitudes of nonaxisymmetric density perturbations $A_m$ as a function of time for individual cos($m\phi$) perturbations. The formula for computing $A_m$ is equation (15) of \citep{boley2006}. Here the integrals are done only over the disk outside 15 AU to suppress contributions from edge effects in the inner disk. The top and bottom panels correspond to the fiducial run (no planet) and the $t = 0$ planet run, respectively.}
\label{fig:Am}
\end{figure}

\begin{figure}[t]
\center
\includegraphics[width=12cm]{Figures/planeta.eps}
\caption{Plot of the planet's radial position as a function of time $\varpi_p(t)$ for the two planet simulations. The dashed-diamond and solid-star lines (colored red and black in the online version) indicate the curves ($\varpi(t)$), points ($a$), and horizontal scales ($t$) that correspond to the $t = 0$ and $t = 10$ planet runs, respectively. The symbols are the approximate semi-major axes $a$ computed for each 0 to 2$\phi$ change in azimuth of the planet as explained in the text.}
\label{fig:a}
\end{figure}

\begin{figure}[t]
\center
\includegraphics[width=12cm]{Figures/planete.eps}
\caption{Plot of the eccentricities $e$, computed for each 0 to 2$\phi$ change in azimuth of the planet as explained in the text, as a function of time. The diamonds and stars (colored red and black in the online version) indicate the points ($e$) and horizontal scales ($t$) that correspond to the $t = 0$ and $t = 10$ planet runs, respectively.}
\label{fig:e}
\end{figure}

>>>>

\begin{thebibliography}{48}
\expandafter\ifx\csname natexlab\endcsname\relax\def\natexlab#1{#1}\fi

\bibitem[{{Baruteau} {et~al.}(2011){Baruteau}, {Meru}, \&
  {Paardekooper}}]{baruteau2011}
{Baruteau}, C., {Meru}, F., \& {Paardekooper}, S.-J. 2011, ArXiv e-prints

\bibitem[{{Boley}(2009)}]{boley2009}
{Boley}, A.~C. 2009, ApJ, 695, L53

\bibitem[{{Boley} \& {Durisen}(2006)}]{boley2006a}
{Boley}, A.~C. \& {Durisen}, R.~H. 2006, ApJ, 641, 534

\bibitem[{{Boley} \& {Durisen}(2008)}]{boley2008}
---. 2008, ApJ, 685, 1193

\bibitem[{{Boley} \& {Durisen}(2010)}]{boley2010b}
---. 2010, \apj, 724, 618

\bibitem[{{Boley} {et~al.}(2007{\natexlab{a}}){Boley}, {Durisen}, {Nordlund},
  \& {Lord}}]{boley2007b}
{Boley}, A.~C., {Durisen}, R.~H., {Nordlund}, {\AA}., \& {Lord}, J.
  2007{\natexlab{a}}, ApJ, 665, 1254

\bibitem[{{Boley} {et~al.}(2007{\natexlab{b}}){Boley}, {Hartquist}, {Durisen},
  \& {Michael}}]{boley2007}
{Boley}, A.~C., {Hartquist}, T.~W., {Durisen}, R.~H., \& {Michael}, S.
  2007{\natexlab{b}}, ApJL, 656, L89

\bibitem[{{Boley} {et~al.}(2010){Boley}, {Hayfield}, {Mayer}, \&
  {Durisen}}]{boley2010}
{Boley}, A.~C., {Hayfield}, T., {Mayer}, L., \& {Durisen}, R.~H. 2010, Icarus,
  207, 509

\bibitem[{{Boley} {et~al.}(2006){Boley}, {Mej{\'{\i}}a}, {Durisen}, {Cai},
  {Pickett}, \& {D'Alessio}}]{boley2006}
{Boley}, A.~C., {Mej{\'{\i}}a}, A.~C., {Durisen}, R.~H., {Cai}, K., {Pickett},
  M.~K., \& {D'Alessio}, P. 2006, ApJ, 651, 517

\bibitem[{{Boss}(2005)}]{boss2005}
{Boss}, A.~P. 2005, ApJ, 629, 535

\bibitem[{{Cai} {et~al.}(2008){Cai}, {Durisen}, {Boley}, {Pickett}, \&
  {Mej{\'{\i}}a}}]{cai2008}
{Cai}, K., {Durisen}, R.~H., {Boley}, A.~C., {Pickett}, M.~K., \&
  {Mej{\'{\i}}a}, A.~C. 2008, ApJ, 673, 1138

\bibitem[{{Cai} {et~al.}(2006){Cai}, {Durisen}, {Michael}, {Boley},
  {Mej{\'{\i}}a}, {Pickett}, \& {D'Alessio}}]{cai2006}
{Cai}, K., {Durisen}, R.~H., {Michael}, S., {Boley}, A.~C., {Mej{\'{\i}}a},
  A.~C., {Pickett}, M.~K., \& {D'Alessio}, P. 2006, ApJL, 636, L149

\bibitem[{{Cai} {et~al.}(2010){Cai}, {Pickett}, {Durisen}, \&
  {Milne}}]{cai2010}
{Cai}, K., {Pickett}, M.~K., {Durisen}, R.~H., \& {Milne}, A.~M. 2010, \apjl,
  716, L176

\bibitem[{{Clarke}(2009)}]{clarke2009}
{Clarke}, C.~J. 2009, MNRAS, 612

\bibitem[{{Cossins} {et~al.}(2009){Cossins}, {Lodato}, \&
  {Clarke}}]{cossins2009}
{Cossins}, P., {Lodato}, G., \& {Clarke}, C.~J. 2009, \mnras, 393, 1157

\bibitem[{{D'Alessio} {et~al.}(2001){D'Alessio}, {Calvet}, \&
  {Hartmann}}]{dalessio2001}
{D'Alessio}, P., {Calvet}, N., \& {Hartmann}, L. 2001, ApJ, 553, 321

\bibitem[{{Dodson-Robinson} {et~al.}(2009){Dodson-Robinson}, {Veras}, {Ford},
  \& {Beichman}}]{dodson2009}
{Dodson-Robinson}, S.~E., {Veras}, D., {Ford}, E.~B., \& {Beichman}, C.~A.
  2009, ApJ, 707, 79

\bibitem[{{Durisen} {et~al.}(2007){Durisen}, {Boss}, {Mayer}, {Nelson},
  {Quinn}, \& {Rice}}]{durisen2007}
{Durisen}, R.~H., {Boss}, A.~P., {Mayer}, L., {Nelson}, A.~F., {Quinn}, T., \&
  {Rice}, W.~K.~M. 2007, Protostars and Planets V, 607

\bibitem[{{Forgan} {et~al.}(2009){Forgan}, {Rice}, {Stamatellos}, \&
  {Whitworth}}]{forgan2009}
{Forgan}, D., {Rice}, K., {Stamatellos}, D., \& {Whitworth}, A. 2009, MNRAS,
  394, 882

\bibitem[{{Gammie}(2001)}]{gammie2001}
{Gammie}, C.~F. 2001, ApJ, 553, 174

\bibitem[{{Goldreich} {et~al.}(2004){Goldreich}, {Lithwick}, \&
  {Sari}}]{goldreich2004}
{Goldreich}, P., {Lithwick}, Y., \& {Sari}, R. 2004, ApJ, 614, 497

\bibitem[{{Hut} {et~al.}(1995){Hut}, {Makino}, \& {McMillan}}]{hut1995}
{Hut}, P., {Makino}, J., \& {McMillan}, S. 1995, ApJL, 443, L93

\bibitem[{{Krumholz} {et~al.}(2007){Krumholz}, {Klein}, \&
  {McKee}}]{krumholz2007}
{Krumholz}, M.~R., {Klein}, R.~I., \& {McKee}, C.~F. 2007, \apj, 656, 959

\bibitem[{{Li} {et~al.}(2001){Li}, {Colgate}, {Wendroff}, \& {Liska}}]{li2001}
{Li}, H., {Colgate}, S.~A., {Wendroff}, B., \& {Liska}, R. 2001, \apj, 551, 874

\bibitem[{{Li} {et~al.}(2000){Li}, {Finn}, {Lovelace}, \& {Colgate}}]{li2000}
{Li}, H., {Finn}, J.~M., {Lovelace}, R.~V.~E., \& {Colgate}, S.~A. 2000, \apj,
  533, 1023

\bibitem[{{Mayer} {et~al.}(2004){Mayer}, {Quinn}, {Wadsley}, \&
  {Stadel}}]{mayer2004}
{Mayer}, L., {Quinn}, T., {Wadsley}, J., \& {Stadel}, J. 2004, ApJ, 609, 1045

\bibitem[{{Mej{\'{\i}}a} {et~al.}(2005){Mej{\'{\i}}a}, {Durisen}, {Pickett}, \&
  {Cai}}]{mejia2005}
{Mej{\'{\i}}a}, A.~C., {Durisen}, R.~H., {Pickett}, M.~K., \& {Cai}, K. 2005,
  ApJ, 619, 1098

\bibitem[{{Meschiari} \& {Laughlin}(2008)}]{meschiari2008}
{Meschiari}, S. \& {Laughlin}, G. 2008, \apjl, 679, L135

\bibitem[{{Michael} \& {Durisen}(2010)}]{michael2010}
{Michael}, S. \& {Durisen}, R.~H. 2010, \mnras, 406, 279

\bibitem[{{Nelson} {et~al.}(2000){Nelson}, {Benz}, \&
  {Ruzmaikina}}]{nelson2000a}
{Nelson}, A.~F., {Benz}, W., \& {Ruzmaikina}, T.~V. 2000, ApJ, 529, 357

\bibitem[{{Paardekooper} {et~al.}(2010){Paardekooper}, {Baruteau}, {Crida}, \&
  {Kley}}]{paardekooper2010}
{Paardekooper}, S., {Baruteau}, C., {Crida}, A., \& {Kley}, W. 2010, \mnras,
  401, 1950

\bibitem[{{Paardekooper} \& {Mellema}(2006)}]{paardekooper2006}
{Paardekooper}, S. \& {Mellema}, G. 2006, A\&A, 459, L17

\bibitem[{{Paardekooper} \& {Papaloizou}(2009)}]{paardekooper2009}
{Paardekooper}, S. \& {Papaloizou}, J.~C.~B. 2009, MNRAS, 394, 2283

\bibitem[{{Paardekooper} {et~al.}(2011){Paardekooper}, {Baruteau}, \&
  {Kley}}]{paardekooper2011}
{Paardekooper}, S.-J., {Baruteau}, C., \& {Kley}, W. 2011, \mnras, 410, 293

\bibitem[{{Papaloizou} {et~al.}(2007){Papaloizou}, {Nelson}, {Kley}, {Masset},
  \& {Artymowicz}}]{papaloizou2007}
{Papaloizou}, J.~C.~B., {Nelson}, R.~P., {Kley}, W., {Masset}, F.~S., \&
  {Artymowicz}, P. 2007, Protostars and Planets V, 655

\bibitem[{{Pickett} {et~al.}(2003){Pickett}, {Mej{\'{\i}}a}, {Durisen},
  {Cassen}, {Berry}, \& {Link}}]{pickett2003}
{Pickett}, B.~K., {Mej{\'{\i}}a}, A.~C., {Durisen}, R.~H., {Cassen}, P.~M.,
  {Berry}, D.~K., \& {Link}, R.~P. 2003, ApJ, 590, 1060

\bibitem[{{Rafikov}(2005)}]{rafikov2005}
{Rafikov}, R.~R. 2005, ApJL, 621, L69

\bibitem[{{Rafikov}(2007)}]{rafikov2007}
---. 2007, ApJ, 662, 642

\bibitem[{{Rafikov}(2009)}]{rafikov2009}
---. 2009, \apj, 704, 281

\bibitem[{{Stamatellos} {et~al.}(2007){Stamatellos}, {Hubber}, \&
  {Whitworth}}]{stamatellos2007}
{Stamatellos}, D., {Hubber}, D.~A., \& {Whitworth}, A.~P. 2007, \mnras, 382,
  L30

\bibitem[{{Stamatellos} \& {Whitworth}(2009)}]{stamatellos2009}
{Stamatellos}, D. \& {Whitworth}, A.~P. 2009, MNRAS, 392, 413

\bibitem[{{Tanaka} {et~al.}(2002){Tanaka}, {Takeuchi}, \& {Ward}}]{tanaka2002}
{Tanaka}, H., {Takeuchi}, T., \& {Ward}, W.~R. 2002, \apj, 565, 1257

\bibitem[{{Vorobyov} \& {Basu}(2006)}]{vorobyov2006}
{Vorobyov}, E.~I. \& {Basu}, S. 2006, ApJ, 650, 956

\bibitem[{{Vorobyov} \& {Basu}(2010{\natexlab{a}})}]{vorobyov2010}
---. 2010{\natexlab{a}}, \apjl, 714, L133

\bibitem[{{Vorobyov} \& {Basu}(2010{\natexlab{b}})}]{vorobyov2010b}
---. 2010{\natexlab{b}}, \apj, 719, 1896

\bibitem[{{Ward} \& {Hahn}(1998)}]{ward1998}
{Ward}, W.~R. \& {Hahn}, J.~M. 1998, AJ, 116, 489

\bibitem[{{Ward} \& {Hahn}(2003)}]{ward2003}
---. 2003, AJ, 125, 3389

\bibitem[{{Zhu} {et~al.}(2010){Zhu}, {Hartmann}, \& {Gammie}}]{zhu2010}
{Zhu}, Z., {Hartmann}, L., \& {Gammie}, C. 2010, ApJ, 713, 1143

\end{thebibliography}

@@

\begin{figure}[t]
\center
\includegraphics[width=11cm]{amt.eps}
\caption{(Color figure available in the online version) Global amplitudes of nonaxisymmetric density perturbations $A_m$ as a function of time for individual cos($m\phi$) perturbations. The formula for computing $A_m$ is equation (15) of \citep{boley2006}. Here the integrals are done only over the disk outside 15 AU to suppress contributions from edge effects in the inner disk. The top and bottom panels correspond to the fiducial run (no planet) and the $t = 0$ planet run, respectively.}
\label{fig:Am}
\end{figure}

\begin{figure}[t]
\center
\includegraphics[width=12cm]{planeta.eps}
\caption{Plot of the planet's radial position as a function of time $\varpi_p(t)$ for the two planet simulations. The dashed-diamond and solid-star lines (colored red and black in the online version) indicate the curves ($\varpi(t)$), points ($a$), and horizontal scales ($t$) that correspond to the $t = 0$ and $t = 10$ planet runs, respectively. The symbols are the approximate semi-major axes $a$ computed for each 0 to 2$\phi$ change in azimuth of the planet as explained in the text.}
\label{fig:a}
\end{figure}

\begin{figure}[t]
\center
\includegraphics[width=12cm]{planete.eps}
\caption{Plot of the eccentricities $e$, computed for each 0 to 2$\phi$ change in azimuth of the planet as explained in the text, as a function of time. The diamonds and stars (colored red and black in the online version) indicate the points ($e$) and horizontal scales ($t$) that correspond to the $t = 0$ and $t = 10$ planet runs, respectively.}
\label{fig:e}
\end{figure}
